An New Search for Supernova Remnants in NGC\,6946

### 2019-01-08 ms.tex
Addition of a sample spectra plto

\todo[inline]{It would probably be good to include a figure showing a few example spectra, as in M83 paper, Fig 3.}

@@

>>>>

Examples of the spectra that were obtained are shown in Fig.\ \ref{fig_example_spectra}.   The three SNRs were selected primarily to show how the quality of the spectra changes as a function of brightness.  The spectroscopically obtained [S II]:\ha\ ratio for L19-048 was 0.45, just above the value for spectroscopic confirmation, while those for the previously known bright object L19-097=MF-015 and the faint candidate L19-096 are higher.  All three SNR candidats show evidence of emission from [O I], which is another indicator that the emission we see arises from shock-heated gas.

@@

\begin{figure}
\plotone{fig_example_spectra.pdf}
\caption{Examples of the spectra obtained for three representative SNR candidates and one H II region.  The three SNR spectra were selected to illustrate the quality of the spectra for a bright, medium bright and fairly faint candidate.  \label{fig_example_spectra}}
\end{figure}
